---
title: "KAD Profiles of K-mers with Unequal KADs in two assemblies"
date: "`r format(Sys.time(), '%d %B %Y')`"
params:
  prefix: NULL
  kdbin: NULL
  kad: NULL
  set1: NULL
  set2: NULL
  binlen: 0.05
  jfversion: null
  version: null
output:
  html_document: default
---

```{r modules, echo = FALSE}
#' Function for calculate cube root value
#' cube root of input numbers (singular or vector) that could be 0, NA,
#' or any positive or negative numbers
cbrt <- function(x) {
  y <- rep(0, length(x))
  not0 <- !is.na(x) & x!=0
  y[is.na(x)] <- NA
  y[not0] <- sign(x[not0]) * exp(log(abs(x[not0])) / 3)
  y
}

#' Function for plotting two KAD curves from k-mers with unequal KADs
diffkadplot <- function(kdfile, transform = c("raw", "cuberoot"),
                        xlabel = "KAD", ylabel = "Counts of k-mers",
                        pmain = "KAD Profiles of unequal KADs",
                        cols = c("red", "darkgreen"), xrange = NULL,
                        yrange = NULL, legendtext = NULL,
                        plotout = FALSE, plotfile = NULL, ...) {
  # check parameters
  stopifnot(sum(transform %in% c("raw", "cuberoot")) >= 1)
  if (length(transform) > 1) { transform = "raw" }
  
  kd <- read.delim(kdfile, stringsAsFactors = F)
  xval <- kd$BIN
  y1 <- kd[, 2]
  y2 <- kd[, 3]
  
  if (transform == "cuberoot") { 
    y1 <- cbrt(y1)
    y2 <- cbrt(y2)
    ylabel <- paste(ylabel, "(cube root)")
  } else if (max(y1, y2) > 1000000000) {
    y1 <- y1 / 1000000000
    y2 <- y2 / 1000000000
    ylabel <- paste(ylabel, "(x10^9)")
  } else if (max(y1, y2) > 1000000) {
    y1 <- y1 / 1000000
    y2 <- y2 / 1000000
    ylabel <- paste(ylabel, "(x1,000,000)")
  }
  
  
  # plot
  if (plotout) {
    if (is.null(plotfile)) {
      plotfile <- gsub(".txt$", "", kdfile)
      plotfile <- paste0(plotfile, ".png")
    }
    #pdf(plotfile, width = 6, height = 5)
    png(plotfile, width = 2.5, height = 2, res = 1200, units = "in", pointsize = 4)
  }
  
  # xrange for plotting
  if (is.null(xrange)) {
    xrange <- range(xval)
  }
  
  # yrange for plotting
  if (is.null(yrange)) {
    yrange <- range(c(y1, y2))
  }
  
  # plot
  plot(NULL, NULL, xlim = xrange, ylim = yrange,
       xlab = xlabel, ylab = ylabel, main = pmain, ...)
  lines(xval, y1, col = cols[1], lwd = 1.5)
  lines(xval, y2, col = cols[2], lwd = 1.5)
  
  # legends:
  if (is.null(legendtext)) {
    legendtext <- colnames(kd)[2:3]
  }
  legend("topleft", legend = legendtext, col = cols,
         bty = "n", lty = 1, lwd = 1.2)
  
  if (plotout) { dev.off() }
}
```


```{r parameters, echo = FALSE}
wd <- params$prefix
s1 <- params$set1
s2 <- params$set2
kad <- params$kad
kdfile <- params$kdbin
binlen <- params$binlen
jfversion <- params$jfversion
scriptversion <- params$version
```

The analysis is to compare k-mer profiles of two sets of sequences, asumming these are two genome assemblies for the same genome. The two assemblies are *`r s1`* and *`r s2`*. From KAD data, k-mers with different copies in the two assemblies were extracted. These k-mers have different KAD values in the two KAD sets. For each KAD set, KAD counts per bin using the bin size as `r binlen` were then determined. These counts were plotted to visualize the differentiation of k-mer profiles of the two assemblies.   

```{r info, echo = FALSE}
library("knitr")
```

### Run environment and KAD script
**R environment**:  
`r version`

**KAD script**:  
KADcompare.pl `r scriptversion`

### INPUT
**assemblies**  
asm1: `r s1`  
asm2: `r s2`  

**counts of k-mer in KAD bins**  
KAD file: `r kad`

### KAD profiles
```{r plot1, echo=F, fig.align='center', fig.cap="Fig 1. KAD profiles", fig.height=6, fig.width= 6}
# input arguments
outbase <- gsub(".*\\/", "", kdfile)
outbase <- gsub("txt$", "", outbase)

# plot PDFs
diffkadplot(kdfile = kdfile, transform = "raw",
            xlabel = "KAD", ylabel = "Counts of k-mers",
            pmain = "KAD Profiles of unequal KADs",
            cols = c("red", "darkgreen"), xrange = NULL,
            yrange = NULL, legendtext = NULL)
```

```{r plot2, echo=F, fig.align='center', fig.cap="Fig 2. KAD profiles", fig.height=6, fig.width= 6}
diffkadplot(kdfile = kdfile, transform = "cuberoot",
            xlabel = "KAD", ylabel = "Counts of k-mers",
            pmain = "KAD Profiles of unequal KADs",
            cols = c("red", "darkgreen"), xrange = NULL,
            yrange = NULL, legendtext = NULL)
```

In the output directory, `r prefix`, both figures were separately generated in PDF format.
